---
title: "Career Beginnings of U.S. Returned Students (1917)"
author: "Cécile Armand"
date: "`r lubridate::today()`"
abstract: |
   This document analyzes the career beginnings of US-educated Chinese using data from the *Who's Who of American returned students* (Tsing Hua, 1917). 
output: html_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)

library(tidyverse)
library(FactoMineR)
library(Factoshiny)
library(networkD3)
```


```{r echo = FALSE}
load("~/Ladder/start.RData")

```

```{r message = FALSE, warning = FALSE}
# Load required packages

library(tidyverse)
library(FactoMineR)
library(Factoshiny)
```

# Data preparation

## Positions
```{r message = FALSE, warning = FALSE, eval = FALSE}

# Load dataset of positions after return

head(career_post)


```

```{r message = FALSE, warning = FALSE}


# Select first position held by individuals 
career_start <- career_post %>% filter(step == "1") # 358 first positions

head(career_start)

```

## Supplementary data
```{r message = FALSE, warning = FALSE}

# birth/attributes
head(main_data_all)

# Education in China (366 curricula)

head(edu_china) 

# Education in USA (810 curricula)

head(edu_us) 

# Work experience in China (PRE-US) (151 positions)

head(position_eng_pre_us) 

# Work experience in the US (134 positions)

head(position_eng_us) 

```
# Basic Analysis 

## Position level
```{r message = FALSE, warning = FALSE}

career_start %>% group_by(level) %>% count() %>% 
  mutate(percent = round(n/358*100, 2)) %>% 
  arrange(desc(n))


```
## Sector of employment
```{r message = FALSE, warning = FALSE}

career_start %>% group_by(sector_code) %>%count() %>% 
  mutate(percent = round(n/358*100, 2)) %>% 
  arrange(desc(n))

```
## Place of employment 
```{r message = FALSE, warning = FALSE}

career_start %>% group_by(area) %>% count() %>% 
  mutate(percent = round(n/358*100, 2)) %>% 
  arrange(desc(n))

```

# Multivariate analysis

In this section, we examine how the level, sector, and location of first positions vary according to generation, place of birth, source of funding, and discipline of specialization. We proceed in three steps: (1) selecting the relevant variables; (2) recoding them, if necessary; and (3) merging these variables with the data on first positions.

```{r message = FALSE, warning = FALSE, eval = FALSE}

# Select relevant data (birth place, return year, source of funding, discipline)
meta_all <- main_data_all %>% select(DocId, Birth_Province_eng_standard, estimated_returned_year, Funding, field2_code)

# Recode disciplines
meta_all <-  main_data_all %>%
  mutate(Discipline = fct_collapse(field2_code,
                                   "Social Sciences" = c("SOC"),
                                   "Humanities" = c("HUM"),
                                   "Multiple" = c("MULTI"),
                                   "Sciences" = c("NAT", "SCI"), 
                                   "Other" = c("MIL", "PROF"), 
                                   "Engineering" = c("ENG")))

meta_all$Discipline <- replace(meta_all$Discipline, is.na(meta_all$Discipline), "Other")

# Recode places of birth

meta_all <- meta_all  %>%
  mutate(Nativeplace = fct_collapse(Birth_Province_eng_standard,
                                    "Jiangsu" = c("Jiangsu"),
                                    "Guangdong" = c("Guangdong"),
                                    "Zhejiang" = c("Zhejiang"),
                                    "Hebei-Zhili" = c("Hebei", "Zhili"), 
                                    "Fujian" = c("Fujian"),
                                    "Hubei" = c("Hubei"),
                                    "Jiangxi" = c("Jiangxi"),
                                    "Other" = c("Anhui", "Sichuan", "Shandong", "Henan", "Hunan", "Gansu", "Guangxi", "Guizhou"), 
                                    "Overseas" = c("Hawaii", "California", "Hongkong", "Malaysia", "New York")))

meta_all$Nativeplace <- replace(meta_all$Nativeplace, is.na(meta_all$Nativeplace), "Other")

# Recode generational cohorts 

## Periodization 1 : Pre/Post Boxer
meta_all$Generation <- cut(meta_all$estimated_returned_year, 
                       breaks = c(0, 1911, 1917),  # Define breakpoints
                       labels = c("PreBoxer", "PostBoxer"),  # Assign labels
                       right = FALSE) 


meta_all$Generation <- replace(meta_all$Generation, is.na(meta_all$Generation), "PreBoxer")

## Pre/Post Examination/Revolution
meta_all$returned_period <- cut(meta_all$estimated_returned_year, 
                       breaks = c(0, 1906, 1912, 1917),  # Define breakpoints
                       labels = c("Pionneer", "PostExam", "PostRevolution"),  # Assign labels
                       right = FALSE) 

meta_all$returned_period <- replace(meta_all$returned_period, is.na(meta_all$returned_period), "PostExam")

meta_all %>% group_by(returned_period) %>% count(sort = TRUE)


```

<div class="alert alert-success" role="alert"> 
Comment on the periodization method. To categorize the student population by generation and cohort based on their year of return, we employ two distinct periodizations. The first is based on Sino–U.S. relations and funding policies, particularly the U.S. remission of the Boxer Indemnity in 1908. We assume that recipients of Boxer Indemnity scholarships returned during the early Republican period, on the premise that their studies required a minimum duration of three years. The second periodization focuses on China’s internal political context, including the reform of the elite selection system marked by the abolition of the imperial examination in 1905, as well as the Xinhai Revolution and the founding of the Republic in 1912.</div> 

```{r message = FALSE, warning = FALSE}

meta_all %>% group_by(Nativeplace) %>% count(sort = TRUE)
meta_all %>% group_by(Discipline) %>% count(sort = TRUE)
meta_all %>% group_by(Generation) %>% count(sort = TRUE)
meta_all %>% group_by(returned_period) %>% count(sort = TRUE)

```

```{r message = FALSE, warning = FALSE, eval = FALSE}
# select recoded data 

meta_all <- meta_all %>% select(DocId, Generation, returned_period, Nativeplace, Funding, Discipline)

# join with career data 

career_start_meta <- inner_join(meta_all, career_start)
```

## Level 

```{r message = FALSE, warning = FALSE}

start_level_cohort_count <- career_start_meta %>% group_by(returned_period, level_code) %>% count()
start_level_cohort_count <- start_level_cohort_count %>% rename(nlevel = n) 
start_level_cohort_count <- left_join(start_level_cohort_count, period_count) 
start_level_cohort_count <- start_level_cohort_count %>% mutate(percent = round(nlevel/n*100, 0)) 

```


```{r message = FALSE, warning = FALSE}

ggplot(start_level_cohort_count, aes(fill=level_code, y=percent, x=returned_period)) + 
  geom_bar(position="dodge", stat="identity")

```


```{r}
```

## Sector over time 

```{r message = FALSE, warning = FALSE, eval = FALSE}
# Sector by period
start_sector_cohort_count <- career_start_meta %>% group_by(returned_period, sector_code) %>% count()
start_sector_cohort_count <- start_sector_cohort_count %>% rename(nsector = n) 
start_sector_cohort_count <- left_join(start_sector_cohort_count, period_count) 
start_sector_cohort_count <- start_sector_cohort_count %>% mutate(percent = round(nsector/n*100, 0)) %>% drop_na(returned_period)

```

```{r message = FALSE, warning = FALSE}

ggplot(start_sector_cohort_count, aes(fill=sector_code, y=percent, x=returned_period)) + 
  geom_bar(position="dodge", stat="identity")

ggplot(start_sector_cohort_count, aes(fill=sector_code, y=percent, x=returned_period)) + 
  geom_bar(stat="identity") + 
  labs(title = "Employment Sector Across Cohorts",
       subtitle = "First Position Upon return", 
       x = "Returned Period")

```


```{r message = FALSE, warning = FALSE, eval = FALSE}

# Occupations by period
start_occup_cohort_count <- career_start_meta %>% group_by(returned_period, level) %>% count()
start_occup_cohort_count <- start_occup_cohort_count %>% rename(nlevel = n) 
start_occup_cohort_count <- left_join(start_occup_cohort_count, period_count) 
start_occup_cohort_count <- start_occup_cohort_count %>% mutate(percent = round(nlevel/n*100, 0)) 

```

```{r message = FALSE, warning = FALSE}

ggplot(start_occup_cohort_count, aes(fill=level, y=percent, x=returned_period)) + 
  geom_bar(stat="identity") + 
  labs(title = "Position Level Across Cohorts",
       subtitle = "First Position Upon return", 
       x = "Returned Period")

```
## Workplace  

```{r message = FALSE, warning = FALSE, eval = FALSE}
start_geo_cohort_count <- career_start_meta %>% group_by(returned_period, area) %>% count()
start_geo_cohort_count <- start_geo_cohort_count %>% rename(ngeo = n) 
start_geo_cohort_count <- left_join(start_geo_cohort_count, period_count) 
start_geo_cohort_count <- start_geo_cohort_count %>% mutate(percent = round(ngeo/n*100, 0)) 

```


```{r message = FALSE, warning = FALSE}

ggplot(start_geo_cohort_count, aes(fill=area, y=percent, x=returned_period)) + 
  geom_bar(stat="identity") + 
  labs(title = "Employment Location Across Cohorts",
       subtitle = "First Position Upon return", 
       x = "Returned Period")


```

# Time elapsed 

In this section, we analyze how the time elapsed between the year of return and the first position varies across cohorts, depending on the return period.
```{r message = FALSE, warning = FALSE, eval = FALSE}

# Plot time elapsed by return period 

start_year <- career_start_meta %>% select(DocId, year)
return_year <- main_data_all %>% select(DocId, estimated_returned_year)
return_start <- inner_join(return_year, start_year)

return_start <- return_start %>% mutate(gap = year-estimated_returned_year)
return_start <- return_start %>% na.omit()

```


```{r message = FALSE, warning = FALSE}

ggplot(return_start, aes(x=estimated_returned_year, y=gap) ) +
  geom_hex(bins = 35) +
  scale_fill_continuous(type = "viridis") +
  theme_bw() + 
  labs(title = "Transition between return and first employment",
       x = "Year of return", 
       y = "Time Elapsed (years)", 
       caption = "Based on 'Who's Who of American Returned Students' (1917)")


library(hrbrthemes)

ggplot(return_start, aes(x=estimated_returned_year, y=gap)) +
  geom_jitter(alpha = 0.6) +
  geom_smooth(method=lm , color="red", fill="#69b3a2", se=TRUE) +
  theme_ipsum()+ 
  labs(
    title = "Transition between return and first employment",
    x = "Year of return", 
    y = "Time Elapsed (years)", 
    caption = "Based on 'Who's Who of American Returned Students' (1917)"
  ) 

```


```{r}
```


# Trajectory analysis

## Did they return to their place of birth? 

### Province 
```{r message = FALSE, warning = FALSE, eval = FALSE}

# we observe at two levels (1) province (2) city

province_start <- career_start %>% select(DocId, province) %>% rename(target = province)
province_birth <- main_data_all %>% select(DocId, Birth_Province_eng_standard) %>% rename(source = Birth_Province_eng_standard)
province_match <- inner_join(province_birth, province_start)

# compute weight 
link1 <- province_match %>% 
  select(source, target) %>%
  group_by(source, target) %>% 
  count() %>% 
  rename(value = "n") %>% drop_na(target)

link1$same <-ifelse(link1$source==link1$target,"TRUE","FALSE")

link12 <-link1 %>% filter(value>1)

node12 <- data.frame(
  name=c(as.character(link12$source), 
         as.character(link12$target)) %>% unique()
)

# create unique id for each connection
link12$IDsource <- match(link12$source, node12$name)-1 
link12$IDtarget <- match(link12$target, node12$name)-1


```

```{r message = FALSE, warning = FALSE}

# Visualize 
library(networkD3)

p1 <- sankeyNetwork(Links = link12, Nodes = node12,
                    Source = "IDsource", Target = "IDtarget",
                    Value = "value", NodeID = "name", 
                    sinksRight=FALSE)
p1

```


```{r message = FALSE, warning = FALSE}

# compare to total births

province_count <- province_match %>% group_by(source) %>% count()

link1 <- left_join(link1, province_count) 
link1 <- link1 %>% mutate(percent = round(value/n*100, 2))

# Detailed list of return loops

link1 %>% filter(same == "TRUE") %>% arrange(desc(value))
link1 %>% filter(same == "TRUE") %>% arrange(desc(percent))
link1 %>% filter(same == "TRUE") %>% arrange(percent)

```
### Town/City

```{r message = FALSE, warning = FALSE, eval = FALSE}

city_start <- career_start %>% select(DocId, city) %>% rename(target = city)
city_birth <- main_data_all %>% select(DocId, Birth_Location_eng_standard) %>% rename(source = Birth_Location_eng_standard)
city_match <- inner_join(city_birth, city_start)

# compute weight 
link2 <- city_match %>% 
  select(source, target) %>%
  group_by(source, target) %>% 
  count() %>% 
  rename(value = "n") %>% drop_na(target)

link2$same <-ifelse(link2$source==link2$target,"TRUE","FALSE")

link22 <-link2 %>% filter(value>1)

node22 <- data.frame(
  name=c(as.character(link22$source), 
         as.character(link22$target)) %>% unique()
)

# create unique id for each connection
link22$IDsource <- match(link22$source, node22$name)-1 
link22$IDtarget <- match(link22$target, node22$name)-1


```

```{r message = FALSE, warning = FALSE}

library(networkD3)

p2 <- sankeyNetwork(Links = link22, Nodes = node22,
                    Source = "IDsource", Target = "IDtarget",
                    Value = "value", NodeID = "name", 
                    sinksRight=FALSE)
p2


```

```{r message = FALSE, warning = FALSE}
# compare to total births
city_count <- city_match %>% group_by(source) %>% count()

link2 <- left_join(link2, city_count) 
link2 <- link2 %>% mutate(percent = round(value/n*100, 2))

# Detailed list of return loops

link2 %>% filter(same == "TRUE") %>% arrange(desc(value))
link2 %>% filter(same == "TRUE") %>% arrange(desc(percent))
link2 %>% filter(same == "TRUE") %>% arrange(percent)
```


## Did they return to teach where they were educated? 

```{r message = FALSE, warning = FALSE}

# Select relevant data

edu_start <- career_start %>% filter(sector_code == "EDU") %>% select(DocId, Institution) %>% rename(Start = Institution)
china_edu <- edu_china %>% rename(education = Institution)
edu_to_start <- left_join(china_edu, edu_start)

# Build a sankey diagram 

edu_to_start_network <- edu_to_start %>% distinct(DocId, education, Start) %>% 
  select(education, Start) %>% rename(source = education, target = Start)

edu_to_start_network <-  edu_to_start_network %>% mutate(source = str_replace_all(source, "Foochow", "Fuzhou"))

# Remove NA and compute weight 
link3 <- edu_to_start_network %>%
  group_by(source, target) %>% 
  count() %>% 
  rename(value = "n") %>% drop_na(target)

link32 <-link3 %>% filter(value>1)

# Create node list from edge list ; the node list contains every entity involved in the flow

node3 <- data.frame(
  name=c(as.character(link32$source), 
         as.character(link32$target)) %>% unique()
)

# Create unique id for each connection
link32$IDsource <- match(link32$source, node3$name)-1 
link32$IDtarget <- match(link32$target, node3$name)-1


```

```{r message = FALSE, warning = FALSE}

# Visualize the strongest flows

library(networkD3)

p3 <- sankeyNetwork(Links = link32, Nodes = node3,
                    Source = "IDsource", Target = "IDtarget",
                    Value = "value", NodeID = "name", 
                    sinksRight=FALSE)
p3


# save the widget (optional)
# library(htmlwidgets)
# saveWidget(p1, file=paste0( getwd(), "~/Media/sankeys/edu_start.html"))

```

```{r message = FALSE, warning = FALSE}

# Detailed list of return loops

link3$same <-ifelse(link3$source==link3$target,"TRUE","FALSE")

link3 %>% filter(same == "TRUE") %>% arrange(desc(value))

```