---
title: "Sequence Analysis of U.S. Returned Students' Careers (1917)"
author: "Cécile Armand"
date: "`r lubridate::today()`"
abstract: |
  This study employs sequence analysis, implemented through the TraMineR library, to examine the career trajectories of US-educated Chinese based on data from the Who’s Who of American Returned Students (Tsinghua, 1917).     

  <style>
    body {
      text-align: justify;
    }
  </style>

output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    number_sections: false
    code_folding: show
    fig_caption: true
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(TraMineR)
library(WeightedCluster)
library(FactoMineR)
library(Factoshiny)
library(forcats)

```

```{r echo=FALSE}

load("~/Ladder/sequence.RData")

```


# Introduction 

After examining career beginnings of U.S.-returned students, the study employs sequence analysis, implemented through the TraMineR library, to examine their subsequent career trajectories. Sequence analysis is conducted across three dimensions: (1) position level, (2) sector of employment, and (3) place of work to examine **vertical, horizontal, and geographical mobility**. Moreover, sequence analysis combines three temporal dimensions: the calendar year of each position, age at the time of the position, and time elapsed since return.

The analysis follows a four-step approach: 

  (1) **Sequence analysis** is applied to the 358 individuals with sufficient career data for each dimension; 
  (2) **Hierarchical clustering** is performed on the resulting sequences to identify recurring career patterns;
  (3) **Multiple Correspondence Analysis (MCA)** is conducted to identify patterns of multidimensional mobility, as well as the influence of biographical and contextual attributes. These attributes are incorporated into the MCA in a second step.
  (4) **Sequence metrics analysis**: To alleviate the shortcomings of sequence clustering analysis and MCA, the final section computes various quantitative indicators for the three sequence series and applies principal component analysis (PCA) to identify clusters of sequences that share similar profiles.
  
# Data preparation 

```{r message = FALSE, warning=FALSE}

# load required packages

library(tidyverse)
library(WeightedCluster)
library(FactoMineR)
library(Factoshiny)
library(forcats)

```


```{r message = FALSE, warning=FALSE}

# load position data

career_seq

```
<br>
The resulting dataset includes a total of 1,001 positions across 263 individuals for whom more than one position is reported, representing 65.6% of the initial population (N = 401).


```{r message = FALSE, warning=FALSE, eval=FALSE}

# load attribute data 

main_data_all <- read_delim("main_data.csv", delim = ";", escape_double = FALSE, trim_ws = TRUE)
main_data_filtered <- main_data_all %>% filter(DocId %in% career_seq$DocId)

```

```{r message = FALSE, warning=FALSE}

main_data_filtered

```

# Sequence Analysis

## Vertical Mobility

### Build sequences
```{r message = FALSE, warning=FALSE}

# Define alphabet, labels and color scheme 

levels <- seqstatl(career_seq$level_code)

levlabels <- c("Other", "Student", "Junior", "Mid-level", 
               "Senior",  "Executive", 
               "Top executive")

levcolor <- c("#78c679", "#4575b4", "#91bfdb", "#e0f3f8", "#fee090", "#fc8d59", "#d73027")

# Create sequence object 

levseq <- seqdef(career_seq, var = c("DocId", "start", "end", "level_code"), 
                 informat = "SPELL", states = levels, labels = levlabels, process = FALSE,  
                 cpal = levcolor)

# Set year of birth as starting point and compute age at position (using the "process" argument)


levseq_birth <- seqdef(career_seq, var = c("DocId", "start", "end", "level_code"), 
                    informat = "SPELL", states = levels, labels = levlabels,
                    process = TRUE, 
                    pdata = main_data_filtered, 
                    pvar = c("DocId", "birth_year"),  
                    cpal = levcolor)


# Focus on the relevant time frame (16-70 y.o.) 

levseq_birth_16 <- levseq_birth[, 16:70]

# Set year of return as starting point

levseq_return <- seqdef(career_seq, var = c("DocId", "start", "end", "level_code"), 
                        informat = "SPELL", states = levels, labels = levlabels,
                        process = TRUE, 
                        pdata = main_data_filtered, 
                        pvar = c("DocId", "estimated_returned_year"),  
                        cpal = levcolor)

# Rename columns 

colnames(levseq_return) <- gsub("^a", "r", colnames(levseq_return))

# Focus on the relevant time frame (1-38 years post-return) 

levseq_return_38 <- levseq_return[, 1:38]

```
<br>
<div class="alert alert-danger" role="alert"> 
Note: '%' represent void elements (beginning or end of sequence) whereas * represent gaps or missing data within sequences.</div>

### Visualize sequences
```{r message = FALSE, warning=FALSE}

# state distribution plots 

par(mar = c(2, 4, 2, 0.5))
par(mfrow = c(2, 2))
seqdplot(levseq, cex.legend=0.7, with.legend = FALSE, border = NA) # based on calendar year
seqdplot(levseq_birth_16, cex.legend=0.7, with.legend = FALSE, border = NA) # based on age at position
seqdplot(levseq_return_38, cex.legend=0.7, with.legend = FALSE, border = NA) # based on time elapsed since return
seqlegend(levseq, cex = 1) # legend

```

### Statistical analyses 
```{r warning=FALSE, message = FALSE}

# number of distinct sequences (210)
seqtab(levseq, idx=0) %>% nrow 

# most frequent sequences 
print(seqtab(levseq))

```

```{r warning=FALSE, message = FALSE}

# Entropy, state and mean time distribution

par(mar = c(2, 2, 2, 0.5))
par(mfrow = c(2, 2))
seqdplot(levseq, with.legend = FALSE, border = NA)  # state distribution plot
seqmsplot(levseq, with.legend = FALSE, border = NA) # modal state plot
seqmtplot(levseq, with.legend = FALSE, ylim=c(0, 2)) # mean time plot
seqHtplot(levseq) # transversal entropy plot 

```

### Distinct subsequences

```{r warning=FALSE, message = FALSE}

# Extract the distinct state-sequence (DSS) for each sequence 

level_dss <- seqdss(levseq)
head(level_dss)
seqtab(level_dss, idx=0) # full list of sub-sequences with their frequencies

# number of distinct sub-sequences
seqtab(level_dss, idx=0) %>% nrow # 74 unique distinct subsequences 
print(seqtab(level_dss))

```


## Horizontal Mobility

### Build sequences 
```{r warning=FALSE, message = FALSE}

# Define alphabet, label and color code 

sector <- seqstatl(career_seq$sector_code)

sector_label <- c("Central Admin", "Local Admin", "Banking", "Education", "Engineering", 
                  "Central Govt", "Local Govt", "Other", "Private", "Railway")

sector_color <- c("#feb24c", "#b2df8a","#6a3d9a", "#fff7bc", "#1f78b4", "#e31a1c", "#31a354", "#b15928", "#cab2d6", "#a6cee3")


# Create sequences

sectseq <- seqdef(career_seq, var = c("DocId", "start", "end", "sector_code"), 
                  informat = "SPELL", process = FALSE, 
                  states = sector, labels = sector_label,  
                  cpal = sector_color)

# set year of birth as starting point and compute age at position (using the "process" argument)

sectseq_birth <- seqdef(career_seq, var = c("DocId", "start", "end", "sector_code"), 
                        informat = "SPELL",
                        process = TRUE, 
                        states = sector, labels = sector_label,  
                        cpal = sector_color,
                        pdata = main_data_filtered, 
                        pvar = c("DocId", "birth_year"))

# focus on the relevant time frame (16-70 y.o.) 

sectseq_birth_16 <- sectseq_birth[, 16:70]

# set year of return as starting point  (using the "process" argument)

sectseq_return <- seqdef(career_seq, var = c("DocId", "start", "end", "sector_code"), 
                        informat = "SPELL", 
                        process = TRUE, 
                        states = sector, labels = sector_label,  
                        cpal = sector_color,
                        pdata = main_data_filtered, 
                        pvar = c("DocId", "estimated_returned_year"))


# rename columns 

colnames(sectseq_return) <- gsub("^a", "r", colnames(sectseq_return))

# focus on the relevant time frame (from 1 to 38 year after return) 

sectseq_return_38 <- sectseq_return[, 1:38]

```

## Visualize sequences

```{r warning=FALSE, message = FALSE}

par(mar = c(2, 4, 2, 0.5))
par(mfrow = c(2, 2))
seqdplot(sectseq, cex.legend=0.7, with.legend = FALSE, border = NA)
seqdplot(sectseq_birth_16, cex.legend=0.7, with.legend = FALSE, border = NA)
seqdplot(sectseq_return_38, cex.legend=0.7, with.legend = FALSE, border = NA)
seqlegend(sectseq, ncol = 1, cex = 1)

```

### Statistical Analysis

```{r warning=FALSE, message = FALSE}

# number of distinct sequences
seqtab(sectseq, idx=0) %>% nrow # 226 unique sequences (out of 263)
print(seqtab(sectseq))

```
```{r warning=FALSE, message = FALSE}

# Entropy, state and mean time distribution

par(mar = c(2, 2, 2, 0.5))
par(mfrow = c(2, 2))
seqdplot(sectseq, with.legend = FALSE, border = NA)
seqmsplot(sectseq, with.legend = FALSE, border = NA)
seqmtplot(sectseq, with.legend = FALSE, ylim=c(0, 2))
seqHtplot(sectseq)

```

```{r warning=FALSE, message = FALSE}

# Distinct subsequences 

sect_dss <- seqdss(sectseq)
head(sect_dss)
seqtab(sect_dss, idx=0) # full list of sub-sequences with their frequencies

# number of distinct sub-sequences
seqtab(sect_dss, idx=0) %>% nrow # 115 unique distinct subsequences 
print(seqtab(sect_dss))


```

## Geographical Mobility

### Build sequences 
```{r warning=FALSE, message = FALSE}

# Define alphabet, labels, and color scheme 

areas <- seqstatl(career_seq$area)
area_label <- c("Overseas", "Beijing-Tianjin", "Guangdong", "Jiangnan", "Other (China)", "Shanghai")
area_color <- c("#91bfdb", "#d53e4f", "#fc8d59", "#fff7bc", "#addd8e", "#c994c7")

# set birth year as starting point 

geoseq_birth <- seqdef(career_seq, var = c("DocId", "start", "end", "area"), 
                 informat = "SPELL", process = TRUE, 
                 states = areas,  
                 labels = area_label,
                 cpal = area_color,
                 pdata = main_data_filtered, 
                 pvar = c("DocId", "birth_year"))

# focus on the relevant time frame (16-60 y.o. 
geoseq_birth_16 <- geoseq_birth[, 16:60]

# set return year as starting point 

geoseq_return <- seqdef(career_seq, var = c("DocId", "start", "end", "area"), 
                       informat = "SPELL", process = TRUE, 
                       states = areas, 
                       labels = area_label,
                       cpal = area_color,
                       pdata = main_data_filtered, 
                       pvar = c("DocId", "estimated_returned_year"))

# rename columns 

colnames(geoseq_return) <- gsub("^a", "r", colnames(geoseq_return))

# focus on the relevant time frame (from 1 to 38 year after return) 
geoseq_return_38 <- geoseq_return[, 1:38]


```

### Visualize sequences 

```{r warning=FALSE, message = FALSE}

par(mar = c(2, 4, 2, 0.5))
par(mfrow = c(2, 2))
seqdplot(geoseq, cex.legend=0.7, with.legend = FALSE, border = NA)
seqdplot(geoseq_birth_16, cex.legend=0.7, with.legend = FALSE, border = NA)
seqdplot(geoseq_return_38, cex.legend=0.7, with.legend = FALSE, border = NA)
seqlegend(geoseq, cex = 1)

```

### Statistical analysis 

```{r warning=FALSE, message = FALSE}

# number of distinct sequences

seqtab(geoseq, idx=0) %>% nrow # 212 unique sequences
print(seqtab(geoseq))


# Entropy, state and mean time distribution

par(mar = c(2, 2, 2, 0.5))
par(mfrow = c(2, 2))
seqdplot(geoseq, with.legend = FALSE, border = NA)
seqmsplot(geoseq, with.legend = FALSE, border = NA)
seqmtplot(geoseq, with.legend = FALSE, ylim=c(0, 2))
seqHtplot(geoseq)

```

### Distinct subsequences

```{r warning=FALSE, message = FALSE}

# Distinct subsequences 

geo_dss <- seqdss(geoseq)
head(geo_dss)
seqtab(geo_dss, idx=0) # full list of sub-sequences with their frequencies

# number of distinct sub-sequences
seqtab(geo_dss, idx=0) %>% nrow # 70 unique distinct subsequences 
print(seqtab(geo_dss))


```

# Clustering 

## Vertical Mobility

```{r warning=FALSE, message = FALSE, eval=FALSE}

# Detect Longest common subsequence (LCS)

level_lcs <- seqdist(levseq, method = "LCS", with.missing=TRUE, norm = "auto") # normalize
level_lcs_sim <- 1 - seqdist(levseq, method = "LCS", with.missing=TRUE, norm = "auto") 

# Clustering using Ward method 

level_lcs_ward <- agnes(level_lcs, diss = TRUE, method = "ward")

```

```{r warning=FALSE, message = FALSE}

par(mfrow = c(1, 1))
plot(level_lcs_ward, which.plots = 2, main = "Hierarchical sequence clustering from the LCS (Ward method)")

```


```{r warning=FALSE, message = FALSE, eval=FALSE}

# Select 10 clusters 

level_lcs_ward10 <- cutree(level_lcs_ward, k = 10)

```


```{r warning=FALSE, message = FALSE}

par(mar = c(2, 4, 2, 0.5))
seqdplot(levseq, group=level_lcs_ward10, border=NA, with.legend = FALSE)
seqfplot(levseq_return_38, group=level_lcs_ward10, border=NA, with.legend = FALSE)

```

```{r warning=FALSE, message = FALSE, eval=FALSE}

# Consolidation with the "partition around medoids" (PAM) method

library(WeightedCluster)

level_lcs_pam10 <- wcKMedoids(level_lcs, k = 10)

```


```{r warning=FALSE, message = FALSE}

par(mar = c(2, 4, 2, 0.5))
seqdplot(levseq, group=level_lcs_pam10$clustering, border=NA, with.legend = FALSE) # state distribution plot
seqfplot(levseq_return_38, group=level_lcs_pam10$clustering, border=NA, with.legend = FALSE) # frequency plot

```

```{r warning=FALSE, message = FALSE, eval = FALSE}

# extract and label clusters
level_cluster <- factor(level_lcs_pam10$clustering)
level_cluster <- as.data.frame(level_cluster)
level_cluster <- rownames_to_column(level_cluster, "level_id")

# retrieve ids 

level_ids <- tibble::rownames_to_column(levseq, "DocId")
level_ids <- tibble::rownames_to_column(level_ids, "level_id")
level_ids <- level_ids[1:2]

# join with names
level_ids_name <- left_join(level_ids, names)

level_cluster <- left_join(level_ids, level_cluster)

# label clusters

library(forcats)

level_cluster <- level_cluster %>% mutate(level_cluster_label = fct_collapse(level_cluster,
                                                                                "High" = c("127", "132", "146", "193", "84"),
                                                                                "Low" = c("182", "29"), 
                                                                                "Medium" = c("25", "74", "219")))


level_cluster %>% group_by(level_cluster) %>% count(sort = TRUE)
level_cluster %>% group_by(level_cluster_label) %>% count(sort = TRUE)


```

## Horizontal Mobility

```{r warning=FALSE, message = FALSE, eval = FALSE}

# Clustering based on Longest common subsequence (LCS)

sector_lcs <- seqdist(sectseq, method = "LCS", with.missing=TRUE, norm = "auto") # normalize
sector_lcs_sim <- 1 - seqdist(sectseq, method = "LCS", with.missing=TRUE, norm = "auto") 

# Clustering using Ward method

library(cluster)
sector_lcs_ward <- agnes(sector_lcs, diss = TRUE, method = "ward")

```


```{r warning=FALSE, message = FALSE}

par(mfrow = c(1, 1))
plot(sector_lcs_ward, which.plots = 2, main = "Hierarchical clustering based on Longest Common Subsequence (LCS), using Ward method")


```


```{r warning=FALSE, message = FALSE, eval = FALSE}

# select 10 clusters

sector_lcs_ward10 <- cutree(sector_lcs_ward, k = 10)

```


```{r warning=FALSE, message = FALSE}

par(mar = c(2, 4, 2, 0.5))
seqdplot(sectseq, group=sector_lcs_ward10, border=NA, with.legend = FALSE)
seqfplot(sectseq_return_38, group=sector_lcs_ward10, border=NA)

```


```{r warning=FALSE, message = FALSE, eval=FALSE}

# Consolidation with the "partition around medoids" (PAM) method

library(WeightedCluster)

sector_lcs_pam10 <- wcKMedoids(sector_lcs, k = 10)

```


```{r warning=FALSE, message = FALSE}

par(mar = c(2, 4, 2, 0.5))
seqdplot(sectseq, group=sector_lcs_pam10$clustering, border=NA, with.legend = FALSE)
seqfplot(sectseq_return_38, group=sector_lcs_pam10$clustering, border=NA, with.legend = FALSE)

```


```{r warning=FALSE, message = FALSE, eval=FALSE}

# extract and label clusters
library(tidyverse)
sector_cluster <- factor(sector_lcs_pam10$clustering)
sector_cluster <- as.data.frame(sector_cluster)
sector_cluster <- rownames_to_column(sector_cluster, "sector_id")

sector_cluster %>% group_by(sector_cluster) %>% count(sort = TRUE)

# retrieve ids 

sector_ids <- tibble::rownames_to_column(sectseq, "DocId")
sector_ids <- tibble::rownames_to_column(sector_ids, "sector_id")
sector_ids <- sector_ids[1:2]

# join with names 

sector_id_name <- left_join(sector_ids, names)

sector_cluster <- left_join(sector_ids, sector_cluster)

# label clusters

sector_cluster <- sector_cluster %>% mutate(sector_cluster_label = fct_collapse(sector_cluster,
                                                                        "Railway" = c("146", "262"),
                                                                        "Education" = c("67", "259", "260"), 
                                                                        "Official" = c("123", "127", "90"), 
                                                                        "Private/Other" = c("132", "157")))

sector_cluster %>% group_by(sector_cluster_label) %>% count(sort = TRUE)

```


## Geographical Mobility 

```{r warning=FALSE, message = FALSE, eval=FALSE}

# Detect Longest common subsequence (LCS)

geo_lcs <- seqdist(geoseq, method = "LCS", with.missing=TRUE, norm = "auto") # normalize
geo_lcs_sim <- 1 - seqdist(geoseq, method = "LCS", with.missing=TRUE, norm = "auto") 

# Clustering using Ward method 

geo_lcs_ward <- agnes(geo_lcs, diss = TRUE, method = "ward")

```


```{r warning=FALSE, message = FALSE}

par(mfrow = c(1, 1))
plot(geo_lcs_ward, which.plots = 2, main = "Hierarchical sequence clustering from the LCS (Ward method)")

```


```{r warning=FALSE, message = FALSE, eval=FALSE}

# Consolidation using the PAM method

library(WeightedCluster)

geo_lcs_pam10 <- wcKMedoids(geo_lcs, k=10)

```


```{r warning=FALSE, message = FALSE}

par(mar = c(2, 4, 2, 0.5))
seqdplot(geoseq, group=geo_lcs_pam10$clustering, border=NA, with.legend = FALSE)
seqfplot(geoseq_return_38, group=geo_lcs_pam10$clustering, border=NA, with.legend = FALSE)

```

```{r warning=FALSE, message = FALSE, eval=FALSE}

# extract and label clusters
geo_cluster <- factor(geo_lcs_pam10$clustering)
geo_cluster <- as.data.frame(geo_cluster)
geo_cluster <- rownames_to_column(geo_cluster, "geo_id")


# retrieve ids 

geo_ids <- tibble::rownames_to_column(geoseq, "DocId")
geo_ids <- tibble::rownames_to_column(geo_ids, "geo_id")
geo_ids <- geo_ids[1:2]

# join with names 

geo_id_name <- left_join(geo_ids, names)

# join with clusters

geo_cluster <- left_join(geo_ids, geo_cluster)

# label clusters

geo_cluster <- geo_cluster %>% mutate(geo_cluster_label = fct_collapse(geo_cluster,
                                                                             "Metropolitan" = c("146", "259", "67"),
                                                                             "Shanghai" = c("250"), 
                                                                             "Jiangnan" = c("1"),
                                                                             "Guangzhou" = c("188"),
                                                                       "Other" = c("263"),
                                                                       "Mobile" = c("29", "148", "260")))

geo_cluster %>% group_by(geo_cluster) %>% count(sort = TRUE)
geo_cluster %>% group_by(geo_cluster_label) %>% count(sort = TRUE)

```

# Multiple Correspondance Analysis

## Data preparation 

```{r warning=FALSE, message = FALSE}

# join clusters from the three dimensions

sector_cluster$sector_id <- NULL
level_cluster$level_id  <- NULL
geo_cluster$geo_id  <- NULL

sector_cluster$sector_cluster <- NULL
level_cluster$level_cluster  <- NULL
geo_cluster$geo_cluster  <- NULL

clusters_ids <- left_join(sector_cluster, level_cluster)
clusters_ids <- left_join(clusters_ids, geo_cluster)

clusters_ids <- clusters_ids %>% rename(sector = sector_cluster_label, level = level_cluster_label, region = geo_cluster_label)

# join with metadata 

meta <- main_data_all %>% select(DocId, Birth_Province_eng_standard, estimated_returned_year, Funding, field2_code)

# regroup/recode variables

meta <- meta  %>%
  mutate(Discipline = fct_collapse(field2_code,
                                "Social Sciences" = c("SOC"),
                                "Humanities" = c("HUM"),
                                "Multiple" = c("MULTI"),
                                "Sciences" = c("NAT", "SCI"), 
                                "Other" = c("MIL", "PROF"), 
                                "Engineering" = c("ENG")))


meta$Discipline <- replace(meta$Discipline, is.na(meta$Discipline), "Other")



meta <- meta  %>%
  mutate(Nativeplace = fct_collapse(Birth_Province_eng_standard,
                                   "Jiangsu" = c("Jiangsu"),
                                   "Guangdong" = c("Guangdong"),
                                   "Zhejiang" = c("Zhejiang"),
                                   "Hebei-Zhili" = c("Hebei", "Zhili"), 
                                   "Other" = c("Fujian", "Hubei", "Jiangxi", "Anhui", "Sichuan", "Shandong", "Henan", "Hunan", "Gansu", "Guangxi"), 
                                   "Overseas" = c("Hawaii", "California", "Hongkong", "Malaysia")))

meta$Nativeplace <- replace(meta$Nativeplace, is.na(meta$Nativeplace), "Other")

meta <- meta  %>%
  mutate(Funding = fct_collapse(Funding,
                                "Public" = c("Government support", "Partial support"),
                                "Private" = c("Private support", "Unknown")))


meta$Generation <- cut(meta$estimated_returned_year, 
                breaks = c(0, 1911, 1917),  # Define breakpoints
                labels = c("PreBoxer", "PostBoxer"),  # Assign labels
                right = FALSE) 


meta$Generation <- replace(meta$Generation, is.na(meta$Generation), "PreBoxer")

names(meta)

meta <- meta %>% select(DocId, Generation, Nativeplace, Funding, Discipline)

names(meta)
summary(meta)

# join with clusters 

cluster_meta <- left_join(meta, clusters_ids)

# prepare data for mca with and without metadata 

cluster_mca <- column_to_rownames(clusters_ids, "DocId")
cluster_meta_mca <- column_to_rownames(cluster_meta, "DocId")

```


## Multidimensional Mobility

```{r warning=FALSE, message = FALSE}

library(FactoMineR)
res.MCA1<-MCA(cluster_mca,graph=FALSE)
plot.MCA(res.MCA1, choix='var',title="MCA Variables Plot",col.var=c(1,2,3))
plot.MCA(res.MCA1,invisible= 'ind',col.var=c(1,1,1,1,2,2,2,3,3,3,3,3,3),title="MCA Biplot with Variables",label =c('var'))
plot.MCA(res.MCA1,invisible= 'var', cex = 0.8, title="MCA Biplot with Individuals",label =c('ind'))

```


```{r warning=FALSE, message = FALSE}

# Hierarchical Clustering (10 dimensions, 8 clusters)

res.MCA1<-MCA(cluster_mca,ncp=10,graph=FALSE)
res.HCPC1<-HCPC(res.MCA1,nb.clust=8,consol=FALSE,graph=FALSE)
plot.HCPC(res.HCPC1,choice='tree',title='Tree')
plot.HCPC(res.HCPC1,choice='map',draw.tree=FALSE,title='Factor Map')
plot.HCPC(res.HCPC1,choice='3D.map',ind.names=FALSE,centers.plot=FALSE,angle=60,title='3D-Tree')
summary(res.HCPC1)

```

## Career and attribute data
```{r warning=FALSE, message = FALSE}

cluster_meta_mca_na <- cluster_meta_mca %>% drop_na(level) %>% drop_na(sector) %>% drop_na(region) 

res.MCA2<-MCA(cluster_meta_mca_na,graph=FALSE)
plot.MCA(res.MCA2, choix='var',title="MCA Variables Plot",col.var=c(1,2,3,4,5,6,7))
plot.MCA(res.MCA2,invisible= 'ind',col.var=c(1,1,2,2,2,2,2,2,3,3,4,4,4,4,4,4,5,5,5,5,6,6,6,7,7,7,7,7,7),title="MCA Biplot with Variables",cex=0.8,cex.main=0.8,cex.axis=0.8,label =c('var'))
plot.MCA(res.MCA2,invisible= 'var',title="MCA Biplot with Individuals",cex=0.8,cex.main=0.8,cex.axis=0.8,label =c('ind'))

```
```{r warning=FALSE, message = FALSE}

# Hierarchical clustering with 4 clusters 

res.MCA2<-MCA(cluster_meta_mca_na,ncp=22,graph=FALSE)
res.HCPC2<-HCPC(res.MCA2,nb.clust=4,consol=FALSE,graph=FALSE)
plot.HCPC(res.HCPC2,choice='tree',title='Tree')
plot.HCPC(res.HCPC2,choice='map',draw.tree=FALSE,title='Factor Map')
plot.HCPC(res.HCPC2,choice='3D.map',ind.names=FALSE,centers.plot=FALSE,angle=60,title='3D-Tree')

```

## Career and affiliation data

See the related scripts for the construction of the supplementary variables and their summary statistics.
```{r warning=FALSE, message = FALSE}

# prepare supplementary variables

sup_var <- meta_clusters %>% select(DocId, Highest_degree, Exam, 
                                    Distinction, Scholarship, 
                                    Work_pre_US, Work_US, 
                                    edu_china_lvc_Label2, 
                                    edu_us_lvc_Label2, us_prestige, 
                                    employ_lvc_cluster_label, 
                                    Activism, assoc_lvc_Label2)

sup_var

sup_var <- sup_var %>% rename(EduChina = edu_china_lvc_Label2, 
                              EduUS = edu_us_lvc_Label2,
                              Employ = employ_lvc_cluster_label, 
                              Assoc = assoc_lvc_Label2)

sup_var_select <- sup_var %>% select(DocId, Highest_degree, 
                                     Exam, Distinction, Scholarship, 
                                     us_prestige, Activism) 

# Join with sequence data

career_cluster_supvar <- left_join(clusters_ids, sup_var)

career_cluster_supvar_select <- career_cluster_supvar %>% select(-c(EduChina, EduUS, Employ, Assoc))

# select relevant variables

career_cluster_supvar_mca <- column_to_rownames(career_cluster_supvar, "DocId")
career_cluster_supvar_select_mca <- column_to_rownames(career_cluster_supvar_select, "DocId")

```

```{r warning=FALSE, message = FALSE}

res.MCA3<-MCA(career_cluster_supvar_select_mca,graph=FALSE)
plot.MCA(res.MCA3, choix='var',title="Graphe des variables",col.var=c(1,2,3,4,5,6,7,8,9,10,11))
plot.MCA(res.MCA3,invisible= 'ind',col.var=c(1,1,1,1,2,2,2,3,3,3,3,3,3,4,4,4,4,4,4,5,5,6,6,7,7,8,8,9,9,10,10,10,11,11,11,11,11),title="Graphe de l'ACM",label =c('var'))

# use explor 
## library(explor)
## explor(res.MCA3)

```
```{r warning=FALSE, message = FALSE}

res.MCA4<-MCA(career_cluster_supvar_mca,graph=FALSE)
plot.MCA(res.MCA4, choix='var',title="Graphe des variables",col.var=c(1,2,3,4,5,6,7,8,9,10,11,12,13,14,15))
plot.MCA(res.MCA4,invisible= 'ind',selectMod= 'cos2 0.1',col.var=c(1,1,1,1,2,2,2,3,3,3,3,3,3,4,4,4,4,4,4,5,5,6,6,7,7,8,8,9,9,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,10,11,11,11,11,11,11,11,11,11,11,11,11,11,11,12,12,12,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,13,14,14,14,14,14,15,15,15,15,15,15,15,15,15,15,15,15,15,15,15,15,15,15),title="Graphe de l'ACM",label =c('var'))

# use explor 
## library(explor)
## explor(res.MCA4)

```


# Sequence metrics

## Compute sequence indices

```{r warning=FALSE, message = FALSE}

# Compute sequence indicators for each dimension/layer 

sector_metrics <- seqindic(sectseq, indic="all", with.missing=F)

level_metrics <- seqindic(levseq, indic="all", with.missing=F)

geo_metrics <- seqindic(geoseq, indic="all", with.missing=F)

# selected metrics (only normalized metrics)

sector_metrics_selected <- sector_metrics %>% select(Visitp, Transp, Entr, MeanD2, Dustd2, Volat, Cplx, Turb2n)
level_metrics_selected <- level_metrics %>% select(Visitp, Transp, Entr, MeanD2, Dustd2, Volat, Cplx, Turb2n)
geo_metrics_selected <- geo_metrics %>% select(Visitp, Transp, Entr, MeanD2, Dustd2, Volat, Cplx, Turb2n)

colnames(sector_metrics_selected) <- paste0("sector.", colnames(sector_metrics_selected))
colnames(level_metrics_selected) <- paste0("level.", colnames(level_metrics_selected))
colnames(geo_metrics_selected) <- paste0("geo.", colnames(geo_metrics_selected))

sector_metrics_selected <- tibble::rownames_to_column(sector_metrics_selected, "DocId")
level_metrics_selected <- tibble::rownames_to_column(level_metrics_selected, "DocId")
geo_metrics_selected <- tibble::rownames_to_column(geo_metrics_selected, "DocId")

# bind columns

metrics_all <- left_join(sector_metrics_selected, level_metrics_selected)
metrics_all <- left_join(metrics_all, geo_metrics_selected)

# Add quality metrics for levels (vertical mobility) 

bad <- seqibad(levseq, with.missing=TRUE, state.order=c('L6','L5','L4','L3', 'L2', 'L1'), state.equiv=list(c('L0')))
bad <- as.data.frame(bad)

degrad <- seqidegrad(levseq, with.missing=TRUE, state.order=c('L6','L5','L4','L3', 'L2', 'L1'), state.equiv=list(c('L0')))
degrad <- as.data.frame(degrad)

insec <- seqinsecurity(levseq, with.missing=TRUE, state.order=c('L6','L5','L4','L3', 'L2', 'L1'), state.equiv=list(c('L0')))
insec <- as.data.frame(insec)

prec <- seqprecarity(levseq, with.missing=TRUE, state.order=c('L6','L5','L4','L3', 'L2', 'L1'), state.equiv=list(c('L0')))
prec <- as.data.frame(prec)

# focus on degradation 

degrad <- tibble::rownames_to_column(degrad, "DocId")

# join with other metrics

metrics_all <- left_join(metrics_all, degrad)

```

```{r warning=FALSE, message = FALSE}

metrics_all

```

## PCA on sequence metrics

```{r warning=FALSE, message = FALSE}

metrics_pca <- column_to_rownames(metrics_all, "DocId")

library(FactoMineR)

res.PCA3<-PCA(metrics_pca,graph=FALSE)
plot.PCA(res.PCA3,choix='var',title="Principal Component Analysis Variables")
plot.PCA(res.PCA3,title="Principal Component Analysis: Individuals")

res.PCA3<-PCA(metrics_pca,ncp=14,graph=FALSE)
res.HCPC3<-HCPC(res.PCA3,nb.clust=3,consol=FALSE,graph=FALSE)
plot.HCPC(res.HCPC3,choice='tree',title='Tree Map')
plot.HCPC(res.HCPC3,choice='map',draw.tree=FALSE,title='Factor Map')
plot.HCPC(res.HCPC3,choice='3D.map',ind.names=FALSE,centers.plot=FALSE,angle=60,title='3D Tree Map')

```
```{r warning=FALSE, message = FALSE}

summary(res.HCPC3)

# extract clusters 

pca_clusters <- res.HCPC3$data.clust
pca_clusters <- rownames_to_column(pca_clusters, "DocId")
pca_clusters <- pca_clusters %>% select(DocId, clust) %>% mutate(mobility = fct_recode(clust, 
                                                                                              "Upward" = "3",
                                                                                              "CrossSector" = "2",
                                                                                              "Moderate" = "1"))

pca_clusters$clust <- NULL

pca_clusters


```
```{r warning=FALSE, message = FALSE}

# join metrics clusters with main data 

career_cluster <- left_join(cluster_meta, pca_clusters)

# extract parangons and specific individuals
res.HCPC3$desc.ind$para
res.HCPC3$desc.ind$dist

```
```{r}

# join with main data (meta) to use as supplementary variables, to check generational effect or other factors

metrics_meta <- inner_join(meta, metrics_all)
metrics_meta_pca <- column_to_rownames(metrics_meta, "DocId")

metrics_biodata <- data.frame(metrics_meta_pca,Generation_Funding=paste0(metrics_meta_pca[,'Generation'],metrics_meta_pca[,'Funding']))
res.PCA4<-PCA(metrics_biodata,ncp=17,quali.sup=c(1,2,3,4,30),graph=FALSE)
plot.PCA(res.PCA4,choix='var',title="Principal Component Analysis Variables")
plot.PCA(res.PCA4,invisible=c('ind','ind.sup'),habillage=1,title="Principal Component Analysis: Individuals",cex=0.75,cex.main=0.75,cex.axis=0.75,label =c('quali'))

```

