---
title: "Career Determinants of U.S. Returned Students (1917)"
author: "Cécile Armand"
date: "`r lubridate::today()`"
tags: [who's who directory, biography, bilingual, histtext, MCA]  
abstract: |
 This document details the construction of the supplementary, synthetic variables used in the Multiple Correspondence Analysis (MCA) of career determinants and provides basic statistical summaries of these variables.
  
  <style>
    body {
    text-align: justify}
  </style>
    
output: 
  html_document:
    toc: true
    toc_float: 
      collapsed: false
      smooth_scroll: false
    toc_depth: 2
    number_sections: false
    code_folding: show # hide
    fig_caption: true
    df_print: paged
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
library(tidyverse)
library(hrbrthemes)
load(file = "~/Ladder/Revised/Scripts/supvariables.RData")

```

```{r warning = FALSE, message = FALSE}

library(tidyverse)
library(hrbrthemes)

```

# Data construction 

## Work experience 

```{r eval = FALSE}

# Before studying in the U.S. 

work_pre <- read_delim("Data/input/work_pre.csv", 
                       delim = ";", escape_double = FALSE, trim_ws = TRUE)

work_pre <- left_join(work_pre, name)

work_pre <- work_pre %>% mutate(Student = paste(DocId, name_source, sep = "_")) %>% 
  mutate(Work_pre_US = "YES") %>% 
  select(Student, Work_pre_US, n, positions) %>% 
  rename(Work_pre_US_Nb = n, Work_pre_US_Nature = positions)

# In the US 

work_us <- read_csv("Data/input/work_us.csv", 
                    col_types = cols(...1 = col_skip()))

work_us <- left_join(work_us, name)

work_us <- work_us %>% mutate(Student = paste(DocId, name_source, sep = "_")) %>% 
  mutate(Work_US = "YES") %>% 
  select(Student, Work_US, n, instit) %>% 
  rename(Work_US_Nb = n, Work_US_Nature = instit)

## Join 

work_experience <- full_join(work_pre, work_us)


```

## Chinese degrees 
```{r eval = FALSE}

chinese_degrees <- read_csv("Data/input/chinese_degrees2.csv")

chinese_degrees <- left_join(chinese_degrees, name)

chinese_degrees <- chinese_degrees %>% mutate(Student = paste(DocId, name_source, sep = "_")) %>% 
  mutate(Exam = "YES") %>% 
  rename(Exam_year = Year) %>%
  select(Student, Exam, Degree_zh, Exam_year)

# join with work experience

exam_work_experience <- full_join(chinese_degrees, work_experience)

exam_work_experience <- exam_work_experience %>%
  mutate(across(c(Exam, Work_pre_US, Work_US), ~replace_na(.x, "NO")))

```

## Highest foreign degree

```{r eval = FALSE}

high_deg_all <- read_csv("Data/input/high_deg_all.csv")

highest_degree <- left_join(high_deg_all, name)

highest_degree <- highest_degree %>% 
  mutate(Student = paste(DocId, name_source, sep = "_")) %>% 
  rename(Highest_degree = Highest) %>% 
  select(Student, Highest_degree)

exam_work_experience <- full_join(exam_work_experience, highest_degree)
```

## Distinctions

```{r eval = FALSE}

# search for distinctions/award, etc

library(histtext)

prize <- histtext::search_concordance_ex('"decoration"|"prize"|"distinction"|"award"|"medal"|"awarded"', 
                                         corpus = "imh-en", context_size = 200, 
                                         filter_query = list(book = "游美同學錄"))


prize %>% group_by(DocId) %>% count(sort = TRUE) %>% print(n = 75)


# total of 146 results were found distributed among 75 individuals, from 1 to 5 each

distinction <- prize %>% group_by(DocId) %>% count() %>% rename(Distinction_Nb = n) 
distinction <- distinction %>% mutate(Distinction = "YES") %>% select(DocId, Distinction, Distinction_Nb)

# join with other data 

distinction <- left_join(distinction, name)

distinction <- distinction %>% 
  mutate(Student = paste(DocId, name_source, sep = "_")) %>% select(Student, Distinction, Distinction_Nb)

exam_work_experience_prize <- full_join(exam_work_experience, distinction)
```

## Scholarships

```{r eval = FALSE}

# search for scholarship, etc

library(histtext)

scholarship <- histtext::search_concordance('"Scholarship"|"Fellowship"', 
                                            corpus = "imh-en", context_size = 200, 
                                            filter_query = list(book = "游美同學錄"))

scholarship_filtered <- scholarship %>%
  filter(grepl("^[A-Z]", Matched))

# a total of 21 results, up to 2 per individual

scholarship %>% group_by(DocId) %>% count(sort = TRUE)

scholarship_count <- scholarship %>% group_by(DocId) %>% count() %>% rename(Scholarship_Nb = n) 
scholarship_count <- scholarship_count %>% mutate(Scholarship = "YES") %>% select(DocId, Scholarship, Scholarship_Nb)

scholarship_count <- left_join(scholarship_count, name)

scholarship_count <- scholarship_count %>% 
  mutate(Student = paste(DocId, name_source, sep = "_")) %>% select(Student, Scholarship, Scholarship_Nb)

scholarship_count$DocId <- NULL

exam_work_experience_prize <- full_join(exam_work_experience_prize, scholarship_count)

# replace NA

exam_work_experience_prize <- exam_work_experience_prize %>%
  mutate(across(c(Exam, Work_pre_US, Work_US, Distinction, Scholarship), ~replace_na(.x, "NO")))


```

## Bind all variables 

```{r eval = FALSE}

# Join with metadata 

meta_add <- main_data_all %>% select(DocId, name_source, FullName_zh, FullName_py, gender)
meta_add <- left_join(meta_all, meta_add)

meta_add <- meta_add %>% 
  mutate(Student = paste(DocId, name_source, sep = "_")) 

meta <- meta_add %>% rename(Gender = gender, Returned_period = returned_period) %>% 
  select(Student, DocId, 
         FullName_zh, FullName_py, 
         Generation, Returned_period, 
         Gender, Nativeplace, 
         Funding, Discipline)

# join with work experience and degrees

exam_work_experience_prize$DocId <- NULL 

meta <- left_join(meta, exam_work_experience_prize)
meta <- meta %>% relocate(Highest_degree, .after = Discipline)

# join with clusters 

library(readr)
edu_china_cluster_lvc <- read_delim("Networks/clusters/edu_china_cluster_lvc.csv", 
                                    delim = ";", escape_double = FALSE, trim_ws = TRUE)

edu_us_cluster_lvc <- read_delim("Networks/clusters/edu_us_cluster_lvc.csv", 
                                 delim = ";", escape_double = FALSE, trim_ws = TRUE)

employ_cluster_lvc <- read_delim("Networks/clusters/employ_cluster_lvc.csv", 
                                 delim = ";", escape_double = FALSE, trim_ws = TRUE)

assoc_cluster_lvc <- read_delim("Networks/clusters/assoc_cluster_lvc.csv", 
                                delim = ";", escape_double = FALSE, trim_ws = TRUE)

edu_us_cluster_lvc <- edu_us_cluster_lvc %>%
  mutate(us_prestige = case_when(
    edu_us_lvc_size < 10 ~ "low",
    edu_us_lvc_size >= 10 & edu_us_lvc_size < 30 ~ "medium",
    edu_us_lvc_size >= 30 ~ "high"))

# join clusters with metadata 

meta_clusters <- left_join(meta, edu_china_cluster_lvc)
meta_clusters <- left_join(meta_clusters, edu_us_cluster_lvc)
meta_clusters <- left_join(meta_clusters, employ_cluster_lvc)
meta_clusters <- left_join(meta_clusters, assoc_cluster_lvc)


meta_clusters <- meta_clusters %>%
  mutate(Funding2 = fct_collapse(as.factor(Funding),
                                 Private = c("Private support", "Unknown"),
                                 Public  = c("Government support", "Partial support")))

meta_clusters <- meta_clusters %>% relocate(Funding2, .after = Funding)

```


# Statistical Summaries


```{r warning = FALSE, message = FALSE}

# Load data and list variables

meta_clusters
main_data_all

```

## Generation/Cohorts

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Generation) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))
meta_clusters %>% group_by(Returned_period) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

```
<br>
<div class="alert alert-success" role="alert"> 
**Note on the periodization**

Taking the Boxer Indemnity Remission as cut-off date: 

  1. Pre-Boxer (1881-1908)
  2. Post-Boxer (1881-1909)
  
A finer periodization based on domestic reforms:  

  1. Pioneers (1881-1905)
  2. Post-examination (1906-1911)
  3. Post-revolution (1912-1917)
</div>

## Gender

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Gender) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

```

## Native Place

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Nativeplace) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))
main_data_all %>% group_by(Birth_Province_eng_standard) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

```

## Funding

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Funding2) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))
meta_clusters %>% group_by(Funding) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

```
## Discipline

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Discipline) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))
main_data_all %>% group_by(field_of_study) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

```
## Degrees

```{r warning = FALSE, message = FALSE}

# What was the highest degree obtained abroad? 
meta_clusters %>% group_by(Highest_degree) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

# Did he/she passed the special examination for returned students? 
meta_clusters %>% group_by(Exam) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

# If yes, when? 
meta_clusters %>% group_by(Exam_year) %>% count(sort = TRUE) 

library(tidyverse)
library(hrbrthemes)

meta_clusters %>% drop_na(Exam_year) %>% 
  ggplot( aes(x=Exam_year)) +
  geom_histogram( binwidth=1, fill="#69b3a2", color="#e9ecef", alpha=0.9) +
  ggtitle("Timeline of Post-return Examinations") +
  theme_ipsum() +
  theme(
    plot.title = element_text(size=15)
  ) +
  labs(x = "Year",
       y = "Frequency", 
       caption = "Source: Who's Who of American-Returned Students (1917)")

# If yes, what equivalent Chinese degree passed did he/she obtained? 

meta_clusters %>% group_by(Degree_zh) %>% count(sort = TRUE) 

```

## Prior Work Experience

### In China

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Work_pre_US) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))
meta_clusters %>% drop_na(Work_pre_US) %>% group_by(Work_pre_US_Nb) %>% count()
meta_clusters %>% group_by(Work_pre_US_Nature) %>% count(sort = TRUE)

```

### In the U.S.

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Work_US) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

# If yes, in which discipline did they major? 

meta_clusters %>% drop_na(Work_US) %>% group_by(Discipline) %>% count(sort = TRUE)

# How many different jobs did they hold? 
meta_clusters %>% group_by(Work_US_Nb) %>% count(sort = TRUE)

# In which sectors? 
meta_clusters %>% group_by(Work_US_Nature) %>% count(sort = TRUE)

```

## Distinction/Scholarship

```{r warning = FALSE, message = FALSE}

# Did they receive special distinctions? 
meta_clusters %>% group_by(Distinction) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

# How many? 
meta_clusters %>% drop_na(Distinction) %>% group_by(Distinction_Nb) %>% count()

# Did they receive special scholarships? 
meta_clusters %>% group_by(Scholarship) %>% count(sort = TRUE) %>% mutate(percent = round(n/401*100, 2))

# How many? 
meta_clusters %>% drop_na(Scholarship) %>% group_by(Scholarship_Nb) %>% count()

```

## Prior Education

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(edu_china_lvc_Label) %>% count(sort = TRUE)
meta_clusters %>% group_by(edu_china_lvc_Label2) %>% count(sort = TRUE)

```

## U.S. Education

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(edu_us_lvc_Label) %>% count(sort = TRUE)
meta_clusters %>% group_by(edu_us_lvc_Label2) %>% count(sort = TRUE)
meta_clusters %>% group_by(us_prestige) %>% count(sort = TRUE)

```

## Post-Return Employment

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(employ_lvc_cluster_label) %>% count(sort = TRUE)

```

## Associative Life

```{r warning = FALSE, message = FALSE}

meta_clusters %>% group_by(Activism) %>% count(sort = TRUE)
meta_clusters %>% group_by(assoc_lvc_Label) %>% count(sort = TRUE)
meta_clusters %>% group_by(assoc_lvc_Label2) %>% count(sort = TRUE)

```
